FTLR proof cases

### 2018-03-13 fully-abstract-comp/ftlr-proof-cases.tex
Add another lemma about loading from a stack capability.
added the missing simple anti-red. lemma

\begin{lemma}[$\lro$ closed under target language antireduction]
  For all $\Phi_S$, $\Phi_T$, $\Phi_T'$, $j$, $n$, if
\[
  \Phi_T \nstep[j] \Phi_T' \text{ and } \npair[n-j]{(\Phi_S,\Phi_T')} \in \lro,
\]
then
\[
  \npair{(\Phi_S,\Phi_T)} \in \lro
\]
\end{lemma}

>>>>

\begin{lemma}[$\lror$ closed under target language antireduction]
  For all $\Phi_S$, $\Phi_T$, $\Phi_T'$, $j$, $n$, if
\[
  \Phi_T \nstep[j] \Phi_T' \text{ and } \npair[n-j]{(\Phi_S,\Phi_T')} \in \lror,
\]
then
\[
  \npair{(\Phi_S,\Phi_T)} \in \lror
\]
\end{lemma}

\begin{lemma}[$\lrol$ closed under target language antireduction]
  For all $\Phi_S$, $\Phi_T$, $\Phi_T'$, $j$, $n$, if
\[
  \Phi_S \nstep[j] \Phi_S' \text{ and } \npair[n-j]{(\Phi_S',\Phi_T)} \in \lrol,
\]
then
\[
  \npair{(\Phi_S,\Phi_T)} \in \lrol
\]
\end{lemma}
